A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
outcome variable section edited

library(tidyverse)
library(here)
library(kableExtra)
library(broom.mixed)
library(knitr)
library(rstanarm)

@@

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
- include summary statistics 
- for every variable in your dataset that is of interest, there needs to be graphs, explanations and tables

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

@@

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

Talk way more about it.

@@

# Model {#sec-model}
For our analysis, we employ a Bayesian generalized linear model (GLM) to forecast the popular vote percentage for Kamala Harris. This approach allows us to capture polling characteristics and account for known variations between pollsters, population types, and the recency of polling data. By incorporating these factors, we aim to model a nuanced estimate of Harris's projected popular vote.

@@

# Results {#sec-results}
To assess model reliability, we examined several key diagnostics. Convergence metrics, such as Rhat values, were close to 1 for all parameters, indicating strong convergence. Additionally, the effective sample size (n_eff) was high across parameters, suggesting low autocorrelation and contributing to model stability. For validation, we conducted out-of-sample testing and calculated the Root Mean Square Error (RMSE) to assess predictive accuracy. This test data, which includes polls not used in training, provides an unbiased estimate of model performance. See more details of model diagnostic here @sec-model-details-diagnostics.

@@

## Weaknesses and Next Steps {#sec-weaknesses}
- if filter thorugh state, data not collected easily

@@

# Appendix {#sec-appendix}
## YouGov Methodology Analysis {#sec-appendix-pollster}

@@

[NTD: ADD MORE DETAILS ABOUT METHODOLOGY]
To allocate the \$100,000 budget, I would budget \$20,000 for a survey platform subscription to handle a large amount of data. I would put \$50,000 into advertising and recruitment for targeted digital ads and phone surveys. I will also use \$20,000 for data analysts and poll aggregation services and \$10,000 for re-contact surveys, contingency costs, and other miscellaneous costs. However, I believe \$100,000 is on the lower end to ensure a high-quality poll and will most likely cost more. Regardless, most of the costs will come from collecting the data, and I have budgeted for this reality (ADD CITATION).

[NTD: ADD THIS AS ANOTHER SECTION]
Please find the proposed question list for the online survey attached here (INSERT URL).

>>>>

library(tidyverse)
library(here)
library(kableExtra)
library(broom.mixed)
library(knitr)
library(kableExtra)
library(rstanarm)

@@

### The Predicted Proportion of Support a Candidate Received in a Poll (%)

The main variable we aim to forecast is the pct variable, which represents the proportion of the vote a candidate received in a poll.@tbl-pct_cleaned and @fig-pct_cleaned shows the summary statistics and distribution of pct variable in a filtered dataset that only comprises of votes from relatively high-quality polling organizations. We also get the popular vote predictions for each candidate using the predict() function and add this to the dataset as the predicted_pct variable. We have showed the summary statistics and distribution for predicted_pct in @tbl-pct_predicted and @fig-pct_predicted, respectively.

Comparing our predictions to the data, our predictions have a smaller range than the cleaned data. While the difference in mean is 2\'%' lower for our prediction than our cleaned data. The results suggest there is less variation in our predictions than the cleaned dataset.

```{r}
#| label: tbl-pct_cleaned
#| fig-cap: Summary statistics for the proportion of support candidates received in the poll
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

# Calculate summary statistics for the 'pct' variable
summary_stats <- cleaned_president_polls %>%
  summarize(
    mean = round(mean(pct, na.rm = TRUE), 2),
    median = round(median(pct, na.rm = TRUE), 2),
    min = round(min(pct, na.rm = TRUE), 2),
    max = round(max(pct, na.rm = TRUE), 2), 
    sd = round(sd(pct, na.rm = TRUE), 2), 
    n = n()

  )

# Create a formatted table to display summary statistics 
summary_stats %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

@@

```{r}
#| label: fig-pct_cleaned
#| fig-cap: Distribution of the proportion of support candidates received in the poll
#| echo: false

# Plot distribution using histogram
ggplot(cleaned_president_polls, aes(x = pct)) + 
  geom_histogram(binwidth = 3, fill = "green", alpha = 0.7, color = "black") +
  theme_minimal() + 
  labs(x = "Percentage of Support (pct)", 
       y = "Count")
```

```{r}
#| label: tbl-pct_predicted
#| fig-cap: Summary statistics for the predicted proportion of support candidates received in the poll
#| echo: false
#| tbl-align: center
#| tbl-width: 82%

# Calculate summary statistics for the 'pct' variable
summary_stats <- prediction %>%
  summarize(
    mean = round(mean(predicted_pct, na.rm = TRUE), 2),
    median = round(median(predicted_pct, na.rm = TRUE), 2),
    min = round(min(predicted_pct, na.rm = TRUE), 2),
    max = round(max(predicted_pct, na.rm = TRUE), 2), 
    sd = round(sd(predicted_pct, na.rm = TRUE), 2), 
    n = n()

  )

# Create a formatted table to display summary statistics 
summary_stats %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

@@

```{r}
#| label: fig-pct_predicted
#| fig-cap: Distribution of the predicted proportion of support candidates received in the poll
#| echo: false
#| fig-width: 5 
#| fig-align: center

# Plot distribution using histogram
ggplot(prediction, aes(x = predicted_pct)) + 
  geom_histogram(binwidth = 3, fill = "green", alpha = 0.7, color = "black") +
  theme_minimal() + 
  labs(x = "Predicted Percentage of Support (predicted_pct)", 
       y = "Count")
```

@@

Pollster

Population Type

Poll Regency (old if data collected in 30 days, old to capture regent old

Separated =between

# Model {#sec-model}

For our analysis, we employ a Bayesian generalized linear model (GLM) to forecast the popular vote percentage for Kamala Harris. This approach allows us to capture polling characteristics and account for known variations between pollsters, population types, and the recency of polling data. By incorporating these factors, we aim to model a nuanced estimate of Harris's projected popular vote.

@@

# Results {#sec-results}

To assess model reliability, we examined several key diagnostics. Convergence metrics, such as Rhat values, were close to 1 for all parameters, indicating strong convergence. Additionally, the effective sample size (n_eff) was high across parameters, suggesting low autocorrelation and contributing to model stability. For validation, we conducted out-of-sample testing and calculated the Root Mean Square Error (RMSE) to assess predictive accuracy. This test data, which includes polls not used in training, provides an unbiased estimate of model performance. See more details of model diagnostic here @sec-model-details-diagnostics.

@@

## Weaknesses and Next Steps {#sec-weaknesses}

-   if filter thorugh state, data not collected easily

@@

# Appendix {#sec-appendix}

## YouGov Methodology Analysis {#sec-appendix-pollster}

@@

\[NTD: ADD MORE DETAILS ABOUT METHODOLOGY\] To allocate the \$100,000 budget, I would budget \$20,000 for a survey platform subscription to handle a large amount of data. I would put \$50,000 into advertising and recruitment for targeted digital ads and phone surveys. I will also use \$20,000 for data analysts and poll aggregation services and \$10,000 for re-contact surveys, contingency costs, and other miscellaneous costs. However, I believe \$100,000 is on the lower end to ensure a high-quality poll and will most likely cost more. Regardless, most of the costs will come from collecting the data, and I have budgeted for this reality (ADD CITATION).

\[NTD: ADD THIS AS ANOTHER SECTION\] Please find the proposed question list for the online survey attached here (INSERT URL).
